\textbf{SPECFEM3D}\\ \textbf{User Manual}

### 2012-09-19 doc/USER_MANUAL/manual_SPECFEM3D.tex
updates the user manual for the definition of an inclined force vector

tilted force, or an impact etc. You will need to give the East, North and vertical components of the force vector;
thus refer to Appendix~\ref{cha:Coordinates} for the orientation of the reference frame.

>>>>

tilted force, or an impact etc. You will need to give the East, North and vertical components of an 
arbitrary (non-unitary) direction vector of the force vector; thus refer to Appendix~\ref{cha:Coordinates} 
for the orientation of the reference frame.
